Uncovering underlying high-level musical content in the time domain \\ \small Leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn deep audio embeddings with applications to MIR downstream tasks

### 2023-06-17 evaluation/evaluation.tex
Updates from Overleaf

\item \textbf{Process each window}: Each window of audio data is processed independently, passed through the pre-trained neural network model, and transformed into an embedding vector. Formally, for each window $w_i$ of audio data, we have:
\begin{equation}
\text{embedding}_i = \text{model}(w_i)
\end{equation}

@@

>>>>

\item \textbf{Process each window}: Each window of audio data is processed independently, passed through the pre-trained neural network, and transformed into an embedding vector. Formally, for each window $w_i$ of audio data, we have:
\begin{equation}
\text{embedding}_i = \text{model}(w_i)
\end{equation}

@@

Employing such embeddings in a traditional music segmentation algorithm can obtain state-of-the-art performance \cite{deepfeaturesegment}

%%%%%%%%%%%%%%%%%%%%%%%%
